Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-14 paper/abstraction/appendix.tex
more edits

\newcommand{\Con}{\mathrm{con}}
\newcommand{\Pfx}{\mathrm{pfx}}%
\newcommand{\CompilePred}{\ensuremath{\mathrm{compile}_\mathrm{pred}}}
\newcommand{\CompilePg}{\ensuremath{\mathrm{compile}_\mathrm{PG}}}
\newcommand{\CompileMbgp}{\ensuremath{\mathrm{compile}_\mathrm{mBGP}}}
\newcommand{\Compile}{\ensuremath{\mathrm{compile}}}
\newcommand{\Append}{\ensuremath{\mathrm{append}}}
\newcommand{\Pref}{\ensuremath{\mathrm{pref}}}
\newcommand{\Topo}{\ensuremath{\mathrm{topo}}}
\newcommand{\EndR}{\ensuremath{\mathrm{end}}}

@@

\subsection{Product Graphs (Step 1)}
In this section, we will establish several relationships between the product graph and preference functions for abstract and concretized \sysname policies. First we relate the languages denoted by regular expressions under concretization. Then we lift this observation to automata, and finally to product graphs.

@@

%\begin{defn}
%If $r$ complies to state machine $M^A$, then we compile the policy $con(r)$ in the following way:%

%  \[ \begin{array}{ll}
%    1. & \sigma^A(q,f(l)) = q' \iff \sigma(q,l) = q' \\
%    2. & q \in F^A \iff q \in F \\
%  \end{array} \]%

%That is, we construct a new automata over the same states and final states, but with a different transition function $\sigma$. This ensures that there is a bisimulation between the two state machines.%

%\end{defn}%
%

%\begin{lem}
%  $M^A$ matches $f(p)$ $\iff$ $M$ matches $p$.
%\end{lem}%

%\begin{proof}
%  Suppose $M^A$ matches $f(p) = A_1, \dots, A_k$, then there exists a trace through $M^A$ of the form:%

%  $$q_0, q_1, \dots, q_{k+1}$$%

%  where $\sigma^A(q_i, A_i) = q_{i+1}$ and $q_{k+1} \in F^A$. We must show that $M$ matches $p = a_1, \dots, a_k$. %

%  From the construction of the automaton, we know that $\sigma(q_i, a_i) = q_{i+1}$ and $q_{k+1} \in F \iff q_{k+1} \in F^A$. Therefore, the trace $q_0, q_1, \dots, q_{k+1}$ is accepted by $M$. 
%  %
%  The same proof is symmetric for the other direction.
%\end{proof}%
%

%\begin{lem}
%  $M$ matches $p$ $\iff$ $p \in \Lang(con(r))$
%  \begin{proof}
%    \[ \begin{array}{lllr}
%      M ~\text{matches}~ p &\iff& M^A ~\text{matches}~ f(p) & \textit{previous lemma} \\
%                         &\iff& f(p) \in \Lang(r) & \textit{automaton construction} \\
%                         &\iff& p \in \Lang(con(r)) & \textit{first lemma} \\
%    \end{array} \]%

%  \end{proof}
%\end{lem}

\vspace{2em}
For the proof, we assume regular expressions are translated to finite automata in a particular way as defined below

@@

\vspace{3em}
For the remainder of this section, we will consider propositions assuming the following: 
%
\[
\begin{array}{lll}
  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) \cap \EndR(L) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f) \cap \EndR(L), G) &=& (t_1, PG, \Pref) \\
  \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
\end{array}
\]
%
where either $L = \Sigma$, or $L = \{ l \}$ with

@@

\begin{defn}
  Because compilation guarantees that the automata states are the same under the concretization function, we can lift the graph homomorphism $f$ to a new homomorphism $f_{pg}$ over the product graph in the following way:
  \[ \begin{array}{rcl}
    f_{pg}( s ) & = & s^A  \\
    f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
  \end{array} \]
\end{defn}

\vspace{1em}
\begin{lem}
  If $f_{pg}(n) = N$, then $P(n) = P^A(N)$.

  \begin{proof}
    Assume $n = (a,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(a),q_1,\dots,q_k)$. 
    We also know that $q_i \in F_i \iff q_i \in F^A_i$. 
    By the definition of the preference function $P$, then $P(n) = P^A(N)$.
  \end{proof}

\vspace{1em}
\begin{lem}
  If, for abstract product graph $PG$, if we have the following:

  \[ \begin{array}{ll}
    1. & (a,b) ~\text{is an edge in the concrete topology} \\
    2. & \tilde{m} = a \\
    3. & f_{pg}(m) = M \\
    4. & (M,N) ~ \text{is an edge in the product graph}~ PG^A \\
    5. & \tilde{N} = f(b) \\
  \end{array} \]

  then there exists a node $n$ in the concrete product graph $PG$ where:

  \[ \begin{array}{ll}
    1. & \tilde{n} = b \\
    2. & f_{pg}(n) = N \\
    3. & (m,n) ~ \text{is an edge in the product graph}~ PG \\
  \end{array} \]

  \begin{proof}

    suppose that $m = (a, q_1, \dots, q_k)$. Then we know that $M = (f(a), q_1, \dots, q_k)$. Also suppose there is some $b$ such that $N = (f(b), s_1, \dots, s_k)$ since $f^{-1}(N) \neq \emptyset$. This means that, since $(a,b)$ is an edge in the concrete topology, $(f(a),f(b))$ is an edge in the abstract topology. Also we know that $\tilde{N} = f(b)$.

    Let us take the node $n = (b, s_1, \dots, s_k)$.

    \begin{easylist}
      & Clearly $\tilde{n} = b$
      & Clearly $f_{pg}(n) = (f(b), s_1, \dots, s_k) = N$
      & For each regular expression $\sigma^A(q_i, f(b)) = s_i$. This means that for each regular expression, $\sigma(q_i, b) = s_i$ if $q_i \neq q_{0_i}$. We know that $q_i \neq q_{0_i}$ due to the side condition for automaton construction. It follows that $(m,n)$ is an edge in the product graph by definition.
    \end{easylist}

>>>>

\newcommand{\Con}{\mathrm{con}}
\newcommand{\Pfx}{\mathrm{pfx}}%
\newcommand{\CompilePred}{\ensuremath{\mathrm{compile}_\mathrm{pred}}}
\newcommand{\CompilePg}{\ensuremath{\mathrm{compile}_\mathrm{PG}}}
\newcommand{\CompileMbgp}{\ensuremath{\mathrm{compile}_\mathrm{mBGP}}}
\newcommand{\Compile}{\ensuremath{\mathrm{compile}}}
\newcommand{\Append}{\ensuremath{\mathrm{append}}}
\newcommand{\Pref}{\ensuremath{\mathrm{pref}}}
\newcommand{\Topo}{\ensuremath{\mathrm{topo}}}
\newcommand{\EndR}{\ensuremath{\mathrm{end}}}
\newcommand{\Rank}{\ensuremath{\mathrm{rank}}}

@@

\subsection{Product Graphs (Step 1)}
In this section, we will establish several relationships between the product graph and preference functions for abstract and concretized \sysname policies. First we relate the languages denoted by regular expressions under concretization. Then we lift this observation to automata, and finally to product graphs. We use these connections to left the notion of homomorphism to the product graphs and to relate the inferred BGP local preferences for abstract and concrete devices.

@@

\vspace{2em}
For the proof, we assume an invariant that when regular expressions are translated to finite automata, there is no transition back to the initial state $q_0$. This is easily done by introducing a separate copy of $q_0$ that allows transitions. The reason is to distinguish if a state corresponds to a router originating a route. We also compile automata in a particular way as defined below

@@

\vspace{3em}
For the remainder of this section, we will prove a collection of lemmas assuming the following: 
%
\[
\begin{array}{lll}
  \CompilePg(t_1 \Path~ \Con(r_1,\Gamma,f) \cap \EndR(L) ~\Prefer~ \ldots ~\Prefer~ \Con(r_n,\Gamma,f) \cap \EndR(L), G) &=& (t_1, PG, \Pref) \\
  \CompilePg(t_2 \Path~ r_1 ~\Prefer~ \ldots ~\Prefer~ r_n, G^A) &=& (t_2, PG^A, \Pref^A) \\
\end{array}
\]
%
We will also assume that $PG = (G',start,rank)$ and $PG^A = (G'^A,start^A,rank^A)$ and that either $L = \Sigma$, or $L = \{ l \}$.

\begin{lem}
  We can lift the homomorphism $f$ to a new homomorphism $f_{pg}$ over the product graphs in the following way:
  \[ \begin{array}{rcl}
    f_{pg}( start ) & = & start^A  \\
    f_{pg}( (l,q_1,\ldots,q_n) ) & = & (f(l),q_1,\ldots,q_n) \\
  \end{array} \]

  We prove that $f_{pg}: G' \rightarrow G'^A$ is a valid homomorphism
  \begin{proof}
    From Lemma 4, we know that $(f(l),q_1,\ldots,q_n)$ is a valid node in $PG^A$ since each automata
    shares the same states. Assume there is an edge in $PG$ from $x=(l,q_1,\ldots,q_n)$
    to $y=(l',q_1',\ldots,q_n')$. We know that $f(x) = (f(l),q_1,\ldots,q_n)$ and $f(y) = (f(l'),q_1',\ldots,q_n')$.
    From the construction of PG, we know that $\sigma_i(q_k, l) = q_k'$. However, from the construction of the abstract automata, we also know that $\sigma_i(q_k, l) = q_k' \iff \sigma^A_i(q_k, f(l)) = q_k'$. Therefore, we can conclude that $\sigma^A_i(q_k, f(l)) = q_k'$. However, from the definition of $PG^A$, this means that there must be an edge in $PG^A$ for ($f(x),f(y)$).
  \end{proof}
\end{lem}

\begin{lem}
  If $f_{pg}(n) = N$, then the product graph preference of these nodes is equal: $\Rank(n) = \Rank^A(N)$.

  \begin{proof}
    Assume $n = (l,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(l),q_1,\dots,q_k)$. 
    We also know that $q_i \in F \iff q_i \in F^A$. 
    By the definition of the ranking function $\Rank$, then 
    $\Rank(n) = \{ i ~\vert~ q_i \in F \} = \{ i ~\vert~ q_i \in F^A \} = \Rank^A(N)$.
  \end{proof}

\begin{lem}
  For every state $N = (L, q_1, \dots, q_n)$ in $PG^A$, there exists a state $n = (l,q_1, \ldots, q_n)$ in $PG$
  such that $f_{pg}(n) = N$.

  \begin{proof}
    By assumption, we assumed that $f$ is surjective. That is, every location $L$ in the original abstract topology $G^A$ is mapped to by at least one location $l$ in the concrete topology $G$: $f(l) = L$. 
  \end{proof}

  \todo{re evaluate this}

  \todo{make explicit the fact that we can't anycast}

  \todo{tie back to existing lemmas}

@@

Next, we show that whenever there is a transition in $PG^A$, there is a corresponding step in the concrete product graph $PG$. This will allows to show that, if the preference inference succeeds for the abstract product graph, then it will also succeed for the concrete product graph while inferring the same preferences.

\begin{lem}
  If, for $PG$ and $PG^A$ we have the following:

  \[ \begin{array}{ll}
    1. & (a,b) ~\text{is an edge in the concrete topology} \\
    2. & \Topo(m) = a \\
    3. & f_{pg}(m) = M \\
    4. & (M,N) ~ \text{is an edge in the product graph}~ PG^A \\
    5. & \Topo(N) = f(b) \\
  \end{array} \]

  then there exists a node $n$ in $PG$ where:

  \[ \begin{array}{ll}
    1. & \Topo(n) = b \\
    2. & f_{pg}(n) = N \\
    3. & (m,n) ~ \text{is an edge in the product graph}~ PG \\
  \end{array} \]

  \begin{proof}
    $ $
    \vspace{1em}

    \noindent
    Since $\Topo(m) = a$, suppose that $m = (a, q_1, \dots, q_k)$. We know that $f_{pg}(m) = M = (f(a), q_1, \dots, q_k)$. By assumption $N = (f(b), s_1, \dots, s_k)$. Let us take the node $n = (b, s_1, \dots, s_k)$.

    \vspace{.8em}
    \begin{easylist}
      & Clearly $\Topo(n) = b$
      & Clearly $f_{pg}(n) = (f(b), s_1, \dots, s_k) = N$
      & Since $(M,N)$ is an edge in $PG^A$, we know that, for each automata transition function: $\sigma^A(q_i, f(b)) = s_i$. From the automata construction, this means that for each regular expression, $\sigma(q_i, b) = s_i$ if $q_i \neq q_{0_i}$. We know that $q_i \neq q_{0_i}$ due to the side condition for automaton construction that ensures no transitions to the initial state. It follows that $(m,n)$ is an edge in the product graph since $(a,b)$ is a valid topology edge by assumption, and $\sigma(q_i, b) = s_i$. 
    \end{easylist}
